\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-12 draft.tex
move sec:tad below sec:foreign
revise proofs for \ga and \pi results

@@

\subsection{Antidumping Duties}
\label{sec:tad}

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.

\vskip.4in
\noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that this derivative is negative. The derivative is 
\begin{equation}
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:pi}
\end{equation}

\vskip.4in
\noindent \textbf{\hypertarget{Pr_pi_indir}{Proof of Lemma~\ref{res:pi_indir}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e}{\partial \pi(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \pi(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
	\]
Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive. $\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.

Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - [\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$. Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.  $\hfill\blacksquare$

@@

>>>>

\bigskip
\subsection{Antidumping Duties}
\label{sec:tad}

@@

@@

@@

\vskip.4in

\newpage
\noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.

The denominator is negative as show in the Proof of Lemma~\ref{res:lobby}. The first term in the numerator is zero since the profit function does not vary in $\ga(\cdot,\cdot)$.

\vskip.4in
\newpage
\noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that the following derivative is negative: 
\begin{equation}
  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:pi}
\end{equation}

This can be simplied to
\[
  \frac{\left(\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
\]

%\noindent $\left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ is always positive.

%Since the denominator is a squared term of a strictly positive quantity, %the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.
$\hfill\blacksquare$

\vskip.2in
\noindent \textbf{\hypertarget{Pr_pi_indir}{Proof of Lemma~\ref{res:pi_indir}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e}{\partial \pi(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \pi(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
	\]
Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive. $\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.

Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is positive by assumption so the first term is positive.

We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tau^a}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.

Then $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} = - \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} \right) = 
	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \pi(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} $
where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. $-\frac{\partial Z(\bta,\tad)}{\partial \pi(
cdot)} = - \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) \leq 0$ by assumption, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \leq 0$. Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.  $\hfill\blacksquare$
